Predicting tree failure likelihood for utility risk mitigation via a novel convolutional neural network

### 2021-02-04 docs/manuscript/manuscript.tex
updated citations.

Predicting the likelihood of failure is an inexact science, but tree risk assessment best management practices have been developed \cite{e.thomassmiley2017best,johnw.goodfellow2020best}. Risk includes assessing the likelihood of failure, the likelihood of impact, and the severity of consequences. The likelihood of failure depends on the anticipated loads on the tree and its load-bearing capacity. The likelihood of impact depends on proximity to the target (the lines, poles, and other hardware---``infrastructure''---in the case of utility tree risk assessment), the target’s occupancy rate (which is constant for utility lines) and whether the target is sheltered, for example by neighboring trees. Severity of consequences depends on the damage done to the infrastructure---which, in turn, is partially related to the size of the tree or tree part that fails, and how much momentum it has when it impacts the infrastructure---and, more importantly in some cases, the economic costs and disruption associated with outages.

@@

We can apply cut-out (occluding portions of the image) for improved performance \cite{devries2017improved}. Also, it has been shown that training with lower resolution improves performance on higher resolution test images \cite{touvronfixing}.

@@

\section{Data Availability Statement}

When submitting a new and revised manuscript, authors are asked to include a data availability statement containing one or more of the following statements, with specific items listed as appropriate. Please include one or more of the statements below, deleting those which do not apply. This section should appear directly before the Acknowledgments section.

\begin{itemize}
\item Some or all data, models, or code generated or used during the study are available in a repository online in accordance with funder data retention policies (provide full citations that include URLS or DOIs)
\item Some or all data, models, or code used during the study were provided by a third party (list items).  Direct requests for these materials may be made to the provider as indicated in the Acknowledgements.
\item Some or all data, models, or code that support the findings of this study are available from the corresponding author upon reasonable request (list items).
\item Some or all data, models, or code generated or used during the study are proprietary or confidential in nature and may only be provided with restrictions (e.g.~anonymized data) (List items and restrictions).
\item All data, models, and code generated or used during the study appear in the submitted article.
\item No data, models, or code were generated or used during the study (e.g., opinion or data-less paper).
\end{itemize}

>>>>

Predicting the likelihood of failure is an inexact science, but tree risk assessment best management practices have been developed \cite{smiley2017best,goodfellow2020best}. Risk includes assessing the likelihood of failure, the likelihood of impact, and the severity of consequences. The likelihood of failure depends on the anticipated loads on the tree and its load-bearing capacity. The likelihood of impact depends on proximity to the target (the lines, poles, and other hardware---``infrastructure''---in the case of utility tree risk assessment), the target’s occupancy rate (which is constant for utility lines) and whether the target is sheltered, for example by neighboring trees. Severity of consequences depends on the damage done to the infrastructure---which, in turn, is partially related to the size of the tree or tree part that fails, and how much momentum it has when it impacts the infrastructure---and, more importantly in some cases, the economic costs and disruption associated with outages.

@@

We can apply cut-out (occluding portions of the image) for improved performance \cite{devries2017improved}. Also, it has been shown that training with lower resolution improves performance on higher resolution test images \cite{touvron2019fixing}.

@@

\section{Data Availability Statement}
All data, models, or code generated or used during the study are available in a repository online in accordance with funder data retention policies (provide full citations that include URLS or DOIs)
